Universal Anonymous Signatures

### 2022-07-26 prism-backend/research/gsac/formal-uas.tex
Migrating from fissue being a predicate to it being a function.

\begin{description}
\item[$\Setup(\secpar) \rightarrow \parm$.] Given a security parameter \secpar,
  returns a global system parameter variable \parm. We assume that \parm are
  available to all the other functions, even if not explicitly listed in their
  input parameters.
\item[$\IKeyGen(\parm,\fissue) \rightarrow (\ipk,\isk)$.] Given \parm, and the
  function \fissue for checking that credential requestors meet the conditions
  to be issued a credential, an issuer runs \IKeyGen to generate its issuing key
  pair. 
\item[$\OKeyGen(\parm,\finsp) \rightarrow (\opk,\osk)$.] Given \parm, and the
  function \finsp, an opener runs \OKeyGen to generate its opening key pair.
  The function \finsp defines the type of utility that will be extractable from
  signatures.
\item[$\UKeyGen(\parm) \rightarrow (\upk,\usk)$.] Given \parm, returns a user's
  key pair.
\item[$\langle
  \Obtain(\usk,\ipk,\sCred,\attrs),
  \Issue(\isk,\sipk,\attrs))  
  \rangle \rightarrow \langle \Cred/\bot,\utrans/\bot
  \rangle$.] %
  This interactive protocol lets a user with key \usk running the \Obtain
  process, receive a credential $\Cred=(\cid,\attrs,\cred,\ipk)$ from an
  issuer in the system, where \cid is a unique identifier for the credential,
  \ipk is the issuer's public key and \cred is the actual credential, on
  attribute set \attrs. The user may leverage a set of previously obtained
  credentials $\sCred=\lbrace (\cid_i,\cattrs_i,\cred_i,\ipk_i)
  \rbrace_{i\in[n]}$, from which we may omit the $\ipk_i$s for readability. The
  user outputs the produced credential \Cred, while the issuer outputs the
  corresponding protocol transcript \utrans.
\item[$\Sign(\usk,\opk,\sCred,\msg,\feval) \rightarrow (\sig,\yeval)$.] %
  Upon receiving a user secret key \usk, opener public key \opk, a set of
  credentials \sCred, a message \msg and evaluation function \feval, returns
  signature \sig, and a plaintext value \yeval. We use use \Sig to denote the
  tuple $(\sig,\yeval)$.
\item[$\Verify(\opk,\sipk,\Sig,\msg,\feval) \rightarrow 1/0$.]
  Checks whether $\Sig = (\sig,\yeval)$ is a valid signature
  over message \msg, from a user with credentials issued by issuers with public
  keys in \sipk, for evaluation function \feval and opener key \opk.
\item[$\Open(\osk,\sipk,\Sig,\msg,\feval) \rightarrow
  (\yinsp,\iproof)/\bot$.]
  Executed by the opener with private key \osk. Receives a signature $\Sig=
  (\sig,\yeval)$ over message \msg and evaluation function \feval,
  generated using credentials issued by the issuers with public keys in \sipk.
  If \Sig is valid, the function outputs a value $\yinsp$, and a proof of
  correct opening \iproof.
\item[$\Judge(\opk,\sipk,\yinsp,\iproof,\Sig,\msg,\feval) \rightarrow 1/0$.] %
  Checks if \iproof is a valid opening correctness proof for the value \yinsp,
  obtained by applying \Open to the the signature $\Sig = (\sig,\yeval)$
  over message \msg, and for evaluation function \feval. 
\end{description}

@@

\begin{description}
\item[$\fissue: ((\upk,\usk),\attrs,\lbrace (\cid_i,\cattrs_i)
  \rbrace_{i \in [n]}) \rightarrow 0/1$.] Chosen
  by each issuer within a family of functions \famfissue, the issuance function
  defines the customized conditions required by the issuer to grant a credential
  over attributes \attrs, when requested by a user with key pair $(\upk,\usk)$,
  leveraging a set of $n$ previously obtained credentials with identifiers and
  attributes given by $\lbrace (\cid_i,\cattrs_i) \rbrace_{i \in [n]}$ (where $n$
  may be $0$ if no previously obtained credential is used). \fissue returns $1$
  to accept a request, $0$ to reject it.
\item[$\feval: ((\upk,\usk),\lbrace(\cid_i,\cattrs_i)\rbrace_{i \in [n]},\msg)
  \rightarrow (\yeval^0,\yeval^1)$.] Signing evaluation functions, from a
  family of functions \famfeval, can be set on a per-signature basis. They
  receive the user key pair $(\upk,\usk)$, a set of credentials with identifiers
  and attributes given by $\lbrace (\cid_i,\cattrs_i) \rbrace_{i \in [n]}$
  (where $n \ge 1$), and the message to be signed \msg. \feval outputs two
  values, $\yeval^0$ and $\yeval^1$, which can be used to modulate the bevahiour
  of \finsp, and must belong in a well defined set \rngfeval. For readability,
  we write $\Yeval = (\yeval^0,\yeval^1)$.
\item[$\finsp: (\Yeval,(\upk,\usk),\lbrace \cid_i,\cattrs_i\rbrace_{i \in [n]},
  \msg) \rightarrow \yinsp$.]
  Chosen by openers from a family of functions \famfinsp. The opening
  functions define what utility value (derived from the user's secret key,
  credentials' identifiers and attributes used for signing, and signed message)
  should be extractable by an opener. Its behaviour can be modulated by \Yeval,
  and it outputs a value \yinsp, which must belong in a well defined set
  \rngfinsp.
\end{description}

@@

\begin{definition}{(\UAS-acceptable functions)}
  \label{def:uas-acc-func}
  We say that a \fissue (similarly, \feval or \finsp) function chosen from some
  family \famfissue (similarly, \famfeval or \famfinsp) is \UAS-acceptable if it
  is one-way with respect to $(\upk,\usk)$. That is, given the output of \fissue
  (similarly, \feval or \finsp), it is at least computationally unfeasible to
  recover the $(\upk,\usk)$ value used to produce it.
\end{definition}

@@

\begin{description}
\item[$\mathsf{H}\lbrace\mathsf{U},\mathsf{I},\mathsf{O} \rbrace$.] Keep
  track of honest users/issuers/openers. They are sets of
  {\uid}s/{\iid}s/{\oid}s.
\item[$\mathsf{C}\lbrace\mathsf{U},\mathsf{I},\mathsf{O} \rbrace$.] Keep
  track of corrupt users/issuers/openers. They are sets of
  {\uid}s/{\iid}s/{\oid}s.    
\item[\UK, \PUBUK and \PRVUK.] \UK maintains user key pairs $(\upk,\usk)$. To
  refer to the key of a specific user, we use $\UK[\uid]$. \PUBUK indexes the
  public keys, and \PRVUK the private keys.
\item[\IK, \PUBIK and \PRVIK.] \IK maintains issuer key pairs, where
  $\IK[\iid]$ refers to the key pair of the issuer with identifier \iid. We
  use \PUBIK to refer to the public component, which also includes the \fissue
  function; and \PRVIK refers to the private component of the key pair.
\item[\OK, \PUBOK, \PRVOK.] Same as \IK, but for opener key pairs. Instead
  of \fissue, \OK includes the \finsp function.
\item[\CRED.] Stores information related to credentials obtained by users in
  the system. Thus, it is indexable by \cid. More specifically, it stores
  tuples of the form $(\uid,\cred,\iid,\attrs,n,\lbrace (\cid_i,\iid_i)
  \rbrace_{i \in [n]})$, where \uid is the identifier of the owner of the
  credential, \cred (when available) is the credential itself, \iid is the
  identifier of the credential issuer, \attrs are the attributes included in
  \cred, $n$ is the number of credentials used to support this request, and
  $(\cid_i,\iid_i)$ for $i \in [n]$ are the corresponding credential and issuer
  identifiers. For notational convenience, we may use $\CRED[\scid]$
  to refer to $\CRED[\cid]$ for all {\cid}s in a set \scid. Also, when clear
  from context, we sometimes use $\CRED[\cid]$ (resp. $\CRED[\scid]$ to
  mean \cred (resp. \scred) in $\CRED[\cid] = (\cdot,\cred,\cdot,\cdot,
  \cdot,\cdot)$ (resp. $\CRED[\scid]$).
\item[\CCRED.] Like \CRED, but keeps track of challenge credentials in the
  issuance anonymity game.
\item[\OWNR.] For notational convenience, when we write $\OWNR[\cid]$ we mean
  ``\uid such that $\CRED[\cid] = (\uid,\cdot,\cdot,\cdot,\cdot,\cdot)$''. We
  may also use \OWNR over a set of {\cid}s (\scid). In that case, our convention
  is that $\OWNR[\scid]$ returns $\bot$ if not all passed {\cid}s belong to the
  same \uid.
\item[\ATTR.] For notational convenience, when we write $\ATTR[\cid]$ we mean
  ``\attrs such that $\CRED[\cid] = (\cdot,\cdot,\cdot,\attrs,\cdot,\cdot)$''.
\item[\ISR.] For notational convenience, when we write $\ISR[\cid]$ we mean
  ``\iid such that $\CRED[\cid] = (\cdot,\cdot,\iid,\cdot,\cdot,\cdot)$''.
\item[\SIG.] Maintains signatures generated via the \SIGN oracle. Entries of
  this table are $(\oid,\scid,\sig,\Yeval,\msg,\feval)$ tuples, where \oid is
  the opener, \scid is the set of identifiers of the credentials used for
  signing, \feval is the signing evaluation function, and \sig and \msg are the
  produced signature and signed message.
\item[\CSIG.] Maintains challenge signatures output to the adversary in the
  signature anonymity game, and is indexable by challenge signatures \csig.
  Each entry contains also $\cuid_b$ and $\cscid_b$, respectively the challenge
  user  and credential identifiers set used to produce \csig; as well as the
  corresponding challenge user and credential set indexed by the complementary
  $1-b$; the signed message \msg and signing evaluation function \feval, the
  result of \feval, \Yeval, and the opener identifier \oid.
\end{description}

@@

        \procedure{$\OBTISS(\cid,\uid,\iid,\attrs,\lbrace (\cid_i,\iid_i)
          \rbrace_{i \in [n]})$}{%
          \pcif \uid \notin \HU: \pcreturn \bot \\
          \pcif \iid \notin \HI: \pcreturn \bot \\
          \pcif \exists i \in [n]~\suchthat~\cid_i \in \CCRED: \pcreturn \bot \\
          \pcif \CRED[\cid] \neq \bot \lor \CCRED[\cid] \neq \bot:
          \pcreturn \bot \\
          \langle \Cred, \utrans \rangle \gets
          \langle \Obtain(\UK[\uid],\CRED[\lbrace \cid_i\rbrace_{i\in[n]}],\attrs), \\
          \hspace*{60pt} \Issue(\PRVIK[\iid],\ISR[\lbrace \cid_i\rbrace_{i\in[n]}],\attrs)
          \rangle \\
          \trans[\cid] \gets \utrans \\
          \CRED[\cid] \gets (\uid, \cred, \iid, \attrs, n,
          \lbrace(\cid_i,\iid_i)\rbrace_{i\in[n]}) \\
          \pcreturn \top \\
        }

        \procedure{$\ISSUE(\cid,\uid,\iid,\attrs,\siid=\lbrace \iid_i
          \rbrace_{i\in[n]})$}{%
          \pcif \uid \notin \CU: \pcreturn \bot \\          
          \pcif \iid \notin \HI: \pcreturn \bot \\
          \pcif \CRED[\cid] \neq \bot \lor \CCRED[\cid] \neq \bot:
          \pcreturn \bot \\
          \langle \cdot, \utrans \rangle \gets
          \langle \adv, 
          \Issue(\PRVIK[\iid],\siid,\attrs) \rangle \\
          \trans[\cid] \gets \utrans \\
          \CRED[\cid] \gets (\uid,\cdot,\iid,\attrs,n,\lbrace(\cdot,\iid_i)
          \rbrace_{i\in[n]}) \\
          \pcreturn \top \\          
        }

        \procedure{$\SIGN(\uid,\oid,\scid=\lbrace\cid_i\rbrace_{i\in[n]},\msg,
          \feval)$}{%
          \pcif \uid \notin \HU: \pcreturn \bot \\
          \pcif \exists i \neq j \in [n]~\suchthat~\cid_i \in \CRED \land
          \cid_j \in \CCRED: \\
          \pcind \pcreturn \bot \\
          \pcif \feval \notin \famfeval: \pcreturn \bot \\
          \Sig \gets \Sign(\UK[\uid],\PUBOK[\oid],\scid,\msg,\feval) \\
          \Yeval=(\yeval^0,\yeval^1) \gets \feval(\UK[\uid],\scid,\msg) \\
          \pcif \Yeval \notin \rngfeval: \pcreturn \bot \\
          \SIG[\uid] \gets \SIG[\uid] \cup
          \lbrace (\oid,\scid,\Sig,\Yeval,\msg,\feval) \rbrace \\
          \pcreturn \Sig \\
        }

@@

        \procedure{$\OBTAIN(\cid,\uid,\iid,\attrs,\lbrace (\cid_i,\iid_i)
          \rbrace_{i\in[n]})$}{%
          \pcif \uid \notin \HU: \pcreturn \bot \\
          \pcif \iid \notin \CI: \pcreturn \bot \\
          \pcif \exists i \in [n]~\suchthat~\cid_i \in \CCRED: \pcreturn \bot \\
          \pcif \CRED[\cid] \neq \bot \lor \CCRED[\cid] \neq \bot: \pcreturn \bot \\
          \langle \Cred, \cdot \rangle \gets
          \langle \Obtain(\UK[\uid],\PUBIK[\iid],\lbrace \cid_i\rbrace_{[n]},
          \attrs),\adv \rangle \\
          \CRED[\cid] \gets (\uid,\cred,\iid,\attrs,n,\lbrace(\cid_i,\iid_i)
          \rbrace_{i\in[n]}) \\
          \pcreturn \top \\
        }

        \procedure{$\OBTCHALb(\cid,\cuid_{0,1},\iid,\attrs,\cscid_{0,1}=$\\
          \hspace*{5.25em}$\lbrace (\ccid_{0,i},\ccid_{1,i}) \rbrace_{i\in[n]})$}{%
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
          \pcif \iid \notin \CI: \pcreturn \bot \\
          \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
          \pcif \exists i\in[n]~\suchthat~
          \PUBIK[\cscid_{0,i}] \neq \PUBIK[\cscid_{1,i}]: \pcreturn \bot \\
          \pcif \pcfor d \in \bin,~ \exists \cid' \in \cscid_d~\suchthat~\cid'
          \in \CRED: \\
          \pcind \pcreturn \bot \\
          \textrm{Parse}~\PUBIK[\iid]~\textrm{as}~((\cdot,\fissue),\cdot) \\
          \pcif \fissue(\UK[\cuid_0],\cscid_0,\attrs) \neq
          \fissue(\UK[\cuid_1],\cscid_1,\attrs) \\
          \langle \Cred, \cdot \rangle \gets
          \langle \Obtain(\UK[\cuid_b],\PUBIK[\iid],\cscid_b,\attrs),\adv \rangle \\
          \CCRED[\ccid_b] \gets (\cuid_b,\cred,\iid,\attrs,\cscid_b,\siid) \\
          \pcreturn \top \\
        }

        \procedure{$\CHALb(\cuid_{0,1},\oid,\cscid_{0,1}=$\\
          \hspace*{5em}$\lbrace (\ccid_{0,i},\ccid_{1,i})
          \rbrace_{i\in[n]},\msg,\feval)$}{%
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
          \pcif \exists i\in[n]~\suchthat~
          \PUBIK[\cscid_{0,i}] \neq \PUBIK[\cscid_{1,i}]: \\
          \pcind \pcreturn \bot \\
          \pcif \feval \notin \famfeval: \pcreturn \bot \\
          \Yeval = (\yeval^0,\yeval^1) \gets \feval(\UK[\cuid_0],\cscid_0,
          \msg) \\
          \TYeval = (\tyeval^0,\tyeval^1) \gets
          \feval(\UK[\cuid_1],\cscid_1,\msg) \\
          \pcif \yeval^0 \neq \tyeval^0: \pcreturn \bot \\
          \pcif \Yeval \notin \rngfeval \lor \TYeval \notin \rngfeval:
          \pcreturn \bot \\          
          \cSig_b \gets \Sign(\UK[\cuid_b],\PUBOK[\oid], \\
          \hspace*{71pt}\cscid_b,\msg,\feval) \\
          \cSig_{1-b} \gets \Sign(\UK[\cuid_{1-b}],\PUBOK[\oid], \\
          \hspace*{80pt}\cscid_{1-b},\msg,\feval) \\          
          \CSIG[\cSig_b] \gets 
          \lbrace (\oid,\cuid_b,\cscid_b,\Yeval,\msg,\feval,\\
          \hspace*{74pt}\cuid_{1-b},\cSig_{1-b},\cscid_{1-b},\TYeval)\rbrace \\
          \pcreturn \cSig_b
        }

@@

\begin{figure}[ht!]
  \centering
  \scalebox{0.9}{
    \input{figures/nizk.tex}
  }
  \caption{CS specification of the NP relations used in \CUASGen.
  \todo{Is $\C = \CCommit(\usk;r)$ needed now that \upk is added?}}
  \label{fig:nizkrels}
\end{figure}

@@

\paragraph{$\usk \gets \UKeyGen(\parm)$.} %
Each user, prior to requesting credentials, generates his secret key by picking
randomly $\usk \getr \AttrSpace$. Set $\upk \gets \CCommit(\usk;0)$.

>>>>

\begin{description}
\item[$\Setup(\secpar) \rightarrow \parm$.] Given a security parameter \secpar,
  returns a global system parameter variable \parm. We assume that \parm are
  available to all the other functions, even if not explicitly listed in their
  input parameters.
\item[$\IKeyGen(\parm,\fissue) \rightarrow (\ipk,\isk)$.] Given \parm, and the
  function \fissue for checking that credential requestors meet the conditions
  to be issued a credential, an issuer runs \IKeyGen to generate its issuing key
  pair. 
\item[$\OKeyGen(\parm,\finsp) \rightarrow (\opk,\osk)$.] Given \parm, and the
  function \finsp, an opener runs \OKeyGen to generate its opening key pair.
  The function \finsp defines the type of utility that will be extractable from
  signatures.
\item[$\UKeyGen(\parm) \rightarrow (\upk,\usk)$.] Given \parm, returns a user's
  key pair.
\item[$\langle
  \Obtain(\usk,\cidu,\ipk,\sCred,\attrs),
  \Issue(\isk,\cidi,\sipk,\attrs))  
  \rangle \rightarrow \langle \Cred/\bot,R/\bot
  \rangle$.] %
  This interactive protocol lets a user with key \usk running the \Obtain
  process, receive a credential $\Cred=(\cid,\attrs,\cred,\ipk)$
  from an issuer in the system. $\cid=(\cidi,\cidu)$ is a unique identifier for
  the credential, where issuer and user randomly pick \cidi and \cidu,
  respectively (to ease notation, whenever we write just \cid, we mean $(\cidi,
  \cidu)$). \ipk is the issuer's public key and \cred is the actual credential,
  on attribute set \attrs. The user may leverage a set of previously obtained
  credentials $\sCred=\lbrace (\cid_i=(\cidi_i,\cidu_i),\cattrs_i,\cred_i,
  \ipk_i)\rbrace_{i\in[n]}$, from which we may omit the $\ipk_i$s for
  readability. The user outputs the produced credential \Cred, while the issuer
  outputs $R \gets (\yissue,\utrans)$, for some value $\yissue$ output by
  the \fissue defined by the issuer, and $\utrans$ being the transcript of
  the communication.
\item[$\Sign(\usk,\opk,\sCred,\msg,\feval) \rightarrow (\sig,\yeval)$.] %
  Upon receiving a user secret key \usk, opener public key \opk, a set of
  credentials \sCred, a message \msg and evaluation function \feval, returns
  signature \sig, and a plaintext value \yeval. We use use \Sig to denote the
  tuple $(\sig,\yeval)$.
\item[$\Verify(\opk,\sipk,\Sig,\msg,\feval) \rightarrow 1/0$.]
  Checks whether $\Sig = (\sig,\yeval)$ is a valid signature
  over message \msg, from a user with credentials issued by issuers with public
  keys in \sipk, for evaluation function \feval and opener key \opk.
\item[$\Open(\osk,\sipk,\Sig,\msg,\feval) \rightarrow
  (\yinsp,\iproof)/\bot$.]
  Executed by the opener with private key \osk. Receives a signature $\Sig=
  (\sig,\yeval)$ over message \msg and evaluation function \feval,
  generated using credentials issued by the issuers with public keys in \sipk.
  If \Sig is valid, the function outputs a value $\yinsp$, and a proof of
  correct opening \iproof.
\item[$\Judge(\opk,\sipk,\yinsp,\iproof,\Sig,\msg,\feval) \rightarrow 1/0$.] %
  Checks if \iproof is a valid opening correctness proof for the value \yinsp,
  obtained by applying \Open to the the signature $\Sig = (\sig,\yeval)$
  over message \msg, and for evaluation function \feval. 
\end{description}

@@

\begin{description}
\item[$\fissue: (\upk,\attrs,\lbrace (\cid_i,\cattrs_i)
  \rbrace_{i \in [n]}) \rightarrow \yissue$.] Chosen
  by each issuer within a family of functions \famfissue, the issuance function
  defines the customized conditions required by the issuer to grant a credential
  over attributes \attrs, when requested by a user with public key \upk,
  leveraging a set of $n$ previously obtained credentials with identifiers and
  attributes given by $\lbrace (\cid_i,\cattrs_i) \rbrace_{i \in [n]}$ (where
  $n$ may be $0$ if no previously obtained credential is used). \fissue returns
  a value $\yissue \in \rngfissue \cup \lbrace 0 \rbrace$, where we adopt the
  convention that $\yissue = 0$ means that the issuance request is denied.
\item[$\feval: (\upk,\lbrace(\cid_i,\cattrs_i)\rbrace_{i \in [n]},\msg)
  \rightarrow (\yeval^0,\yeval^1)$.] Signing evaluation functions, from a
  family of functions \famfeval, can be set on a per-signature basis. They
  receive the user public key \upk, a set of credentials with identifiers
  and attributes given by $\lbrace (\cid_i,\cattrs_i) \rbrace_{i \in [n]}$
  (where $n \ge 1$), and the message to be signed \msg. \feval outputs two
  values, $\yeval^0$ and $\yeval^1$, which can be used to modulate the bevahiour
  of \finsp, and must belong in a well defined set \rngfeval. For readability,
  we write $\Yeval = (\yeval^0,\yeval^1)$.
\item[$\finsp: (\Yeval,\upk,\lbrace \cid_i,\cattrs_i\rbrace_{i \in [n]},
  \msg) \rightarrow \yinsp$.]
  Chosen by openers from a family of functions \famfinsp. The opening
  functions define what utility value (derived from the user's secret key,
  credentials' identifiers and attributes used for signing, and signed message)
  should be extractable by an opener. Its behaviour can be modulated by \Yeval,
  and it outputs a value \yinsp, which must belong in a well defined set
  \rngfinsp.
\end{description}

@@

% \begin{definition}{(\UAS-acceptable functions)}
%   \label{def:uas-acc-func}
%   We say that a \fissue (similarly, \feval or \finsp) function chosen from some
%   family \famfissue (similarly, \famfeval or \famfinsp) is \UAS-acceptable if it
%   is one-way with respect to $(\upk,\usk)$. That is, given the output of \fissue
%   (similarly, \feval or \finsp), it is at least computationally unfeasible to
%   recover the $(\upk,\usk)$ value used to produce it.
% \end{definition}

@@

\begin{description}
\item[$\mathsf{H}\lbrace\mathsf{U},\mathsf{I},\mathsf{O} \rbrace$.] Keep
  track of honest users/issuers/openers. They are sets of
  {\uid}s/{\iid}s/{\oid}s.
\item[$\mathsf{C}\lbrace\mathsf{U},\mathsf{I},\mathsf{O} \rbrace$.] Keep
  track of corrupt users/issuers/openers. They are sets of
  {\uid}s/{\iid}s/{\oid}s.    
\item[\UK, \PUBUK and \PRVUK.] \UK maintains user key pairs $(\upk,\usk)$. To
  refer to the key of a specific user, we use $\UK[\uid]$. \PUBUK indexes the
  public keys, and \PRVUK the private keys.
\item[\IK, \PUBIK and \PRVIK.] \IK maintains issuer key pairs, where
  $\IK[\iid]$ refers to the key pair of the issuer with identifier \iid. We
  use \PUBIK to refer to the public component, which also includes the \fissue
  function; and \PRVIK refers to the private component of the key pair.
\item[\OK, \PUBOK, \PRVOK.] Same as \IK, but for opener key pairs. Instead
  of \fissue, \OK includes the \finsp function.
\item[\CRED.] Stores information related to credentials obtained by users in
  the system. Thus, it is indexable by \cid. More specifically, it stores
  tuples of the form $(\uid,\cred,\iid,\attrs,n,\lbrace (\cid_i,\iid_i)
  \rbrace_{i \in [n]})$, where \uid is the identifier of the owner of the
  credential, \cred (when available) is the credential itself, \iid is the
  identifier of the credential issuer, \attrs are the attributes included in
  \cred, $n$ is the number of credentials used to support this request, and
  $(\cid_i,\iid_i)$ for $i \in [n]$ are the corresponding credential and issuer
  identifiers. For notational convenience, we may use $\CRED[\scid]$
  to refer to $\CRED[\cid]$ for all {\cid}s in a set \scid. Also, when clear
  from context, we sometimes use $\CRED[\cid]$ (resp. $\CRED[\scid]$ to
  mean \cred (resp. \scred) in $\CRED[\cid] = (\cdot,\cred,\cdot,\cdot,
  \cdot,\cdot)$ (resp. $\CRED[\scid]$).
\item[\CCRED.] Like \CRED, but keeps track of challenge credentials in the
  issuance anonymity game.
\item[\OWNR.] For notational convenience, when we write $\OWNR[\cid]$ we mean
  ``\uid such that $\CRED[\cid] = (\uid,\cdot,\cdot,\cdot,\cdot,\cdot)$''. We
  may also use \OWNR over a set of {\cid}s (\scid). In that case, our convention
  is that $\OWNR[\scid]$ returns $\bot$ if not all passed {\cid}s belong to the
  same \uid. Since $\bot$ is not a valid \uid, all conditions checking
  membership of the output of \OWNR to a list of users equal false if \OWNR
  returns $\bot$.
\item[\ATTR.] For notational convenience, when we write $\ATTR[\cid]$ we mean
  ``\attrs such that $\CRED[\cid] = (\cdot,\cdot,\cdot,\attrs,\cdot,\cdot)$''.
\item[\ISR.] For notational convenience, when we write $\ISR[\cid]$ we mean
  ``\iid such that $\CRED[\cid] = (\cdot,\cdot,\iid,\cdot,\cdot,\cdot)$''.
\item[\SIG.] Maintains signatures generated via the \SIGN oracle. Entries of
  this table are $(\oid,\scid,\sig,\Yeval,\msg,\feval)$ tuples, where \oid is
  the opener, \scid is the set of identifiers of the credentials used for
  signing, \feval is the signing evaluation function, and \sig and \msg are the
  produced signature and signed message.
\item[\CSIG.] Maintains challenge signatures output to the adversary in the
  signature anonymity game, and is indexable by challenge signatures \csig.
  Each entry contains also $\cuid_b$ and $\cscid_b$, respectively the challenge
  user  and credential identifiers set used to produce \csig; as well as the
  corresponding challenge user and credential set indexed by the complementary
  $1-b$; the signed message \msg and signing evaluation function \feval, the
  result of \feval, \Yeval, and the opener identifier \oid.
\end{description}

@@

        \procedure{$\OBTISS(\cid=(\cidi,\cidu),\uid,\iid,\attrs,$\\
          \hspace*{4.25em}$\lbrace (\cid_i,\iid_i) \rbrace_{i \in [n]})$}{%
          \pcif \uid \notin \HU \lor \iid \notin \HI: \pcreturn \bot \\
          \pcif \exists i \in [n]~\suchthat~\cid_i \in \CCRED: \pcreturn \bot \\
          \pcif \CRED[\cid] \neq \bot \lor \CCRED[\cid] \neq \bot:
          \pcreturn \bot \\
          \langle \Cred, R \rangle \gets
          \langle \Obtain(\UK[\uid],\cidu,\CRED[\lbrace \cid_i\rbrace_{i\in[n]}],\attrs), \\
          \hspace*{50pt} \Issue(\PRVIK[\iid],\cidi,\ISR[\lbrace \cid_i\rbrace_{i\in[n]}],\attrs)
          \rangle \\
          \trans[\cid] \gets R \\
          \CRED[\cid] \gets (\uid, \cred, \iid, \attrs, n,
          \lbrace(\cid_i,\iid_i)\rbrace_{i\in[n]}) \\
          \pcreturn \top \\
        }

        \procedure{$\ISSUE(\cidi,\uid,\iid,\attrs,\siid=
          \lbrace \iid_i\rbrace_{i\in[n]})$}{%
          \pcif \uid \notin \CU \lor \iid \notin \HI: \pcreturn \bot \\
          \pcif \CRED[(\cidi,\cdot)] \neq \bot \lor \CCRED[(\cidi,\cdot)]
          \neq \bot: \\
          \pcind \pcreturn \bot \\
          \langle \cdot, R \rangle \gets
          \langle \adv, 
          \Issue(\PRVIK[\iid],\cidi,\siid,\attrs) \rangle \\
          \trans[(\cidi,\cdot)] \gets R \\
          \CRED[(\cidi,\cdot)] \gets (\uid,\cdot,\iid,\attrs,n,\lbrace(\cdot,
          \iid_i)
          \rbrace_{i\in[n]}) \\
          \pcreturn \top \\          
        }

        \procedure{$\SIGN(\uid,\oid,\scid=\lbrace\cid_i\rbrace_{i\in[n]},\msg,
          \feval)$}{%
          \pcif \uid \notin \HU \lor \feval \notin \famfeval: \pcreturn \bot \\
          \pcif \exists i \neq j \in [n]~\suchthat~\cid_i \in \CRED \land
          \cid_j \in \CCRED: \\
          \pcind \pcreturn \bot \\
          \Sig \gets \Sign(\UK[\uid],\PUBOK[\oid],\scid,\msg,\feval) \\
          \Yeval=(\yeval^0,\yeval^1) \gets \feval(\UK[\uid],\scid,\msg) \\
          \SIG[\uid] \gets \SIG[\uid] \cup
          \lbrace (\oid,\scid,\Sig,\Yeval,\msg,\feval) \rbrace \\
          \pcreturn \Sig \\
        }

@@

        \procedure{$\OBTAIN(\cidu,\uid,\iid,\attrs,\lbrace (\cid_i,\iid_i)
          \rbrace_{i\in[n]})$}{%
          \pcif \uid \notin \HU \lor \iid \notin \CI: \pcreturn \bot \\
          \pcif \exists i \in [n]~\suchthat~\cid_i \in \CCRED: \pcreturn \bot \\
          \pcif \CRED[(\cdot,\cidu)] \neq \bot \lor \CCRED[(\cidu,\cdot)] \neq
          \bot: \\
          \pcind \pcreturn \bot \\
          \langle \Cred, \cdot \rangle \gets
          \langle \Obtain(\UK[\uid],\cidu,\PUBIK[\iid],\lbrace \cid_i\rbrace_{[n]},
          \attrs),\adv \rangle \\
          \CRED[(\cdot,\cidu)] \gets (\uid,\cred,\iid,\attrs,n,\lbrace(\cid_i,
          \iid_i) \rbrace_{i\in[n]}) \\
          \pcreturn \top \\
        }

        \procedure{$\OBTCHALb(\cidu,\cuid_{0,1},\iid,\attrs,\cscid_{0,1}=$\\
          \hspace*{5.25em}$\lbrace (\ccid_{0,i},\ccid_{1,i}) \rbrace_{i\in[n]})$}{%
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
          \pcif \iid \notin \CI: \pcreturn \bot \\
          \pcif \CRED[(\cdot,\cidu)] \neq \bot: \pcreturn \bot \\
          \pcif \exists i\in[n]~\suchthat~
          \PUBIK[\cscid_{0,i}] \neq \PUBIK[\cscid_{1,i}]: \pcreturn \bot \\
          \pcif \pcfor d \in \bin,~ \exists \cid' \in \cscid_d~\suchthat~\cid'
          \in \CRED: \\
          \pcind \pcreturn \bot \\
          \textrm{Parse}~\PUBIK[\iid]~\textrm{as}~((\cdot,\fissue),\cdot) \\
          \pcif 0(\fissue(\PUBUK[\cuid_0],\cscid_0,\attrs)) \neq \\
          \pcind 0(\fissue(\PUBUK[\cuid_1],\cscid_1,\attrs)): \pcreturn \bot \\
          \langle \Cred, \cdot \rangle \gets
          \langle \Obtain(\PRVUK[\cuid_b],\cidu,\PUBIK[\iid],\cscid_b,\attrs),
          \adv \rangle \\
          \CCRED[(\cdot,\cidu)] \gets (\cuid_b,\cred,\iid,\attrs,\cscid_b,\siid) \\
          \pcreturn \top \\
        }

        \procedure{$\CHALb(\cuid_{0,1},\oid,\cscid_{0,1}=$\\
          \hspace*{5em}$\lbrace (\ccid_{0,i},\ccid_{1,i})
          \rbrace_{i\in[n]},\msg,\feval)$}{%
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
          \pcif \exists i\in[n]~\suchthat~
          \PUBIK[\cscid_{0,i}] \neq \PUBIK[\cscid_{1,i}]: \\
          \pcind \pcreturn \bot \\
          \pcif \feval \notin \famfeval: \pcreturn \bot \\
          \Yeval = (\yeval^0,\yeval^1) \gets \feval(\PUBUK[\cuid_0],\cscid_0,
          \msg) \\
          \TYeval = (\tyeval^0,\tyeval^1) \gets
          \feval(\PUBUK[\cuid_1],\cscid_1,\msg) \\
          \pcif \yeval^0 \neq \tyeval^0: \pcreturn \bot \\   
          \cSig_b \gets \Sign(\PRVUK[\cuid_b],\PUBOK[\oid],\cscid_b,\msg,
          \feval) \\
          \cSig_{1-b} \gets \Sign(\PRVUK[\cuid_{1-b}],\PUBOK[\oid],\cscid_{1-b},\msg,\feval) \\          
          \CSIG[\cSig_b] \gets 
          \lbrace (\oid,\cuid_b,\cscid_b,\Yeval,\msg,\feval,\\
          \hspace*{74pt}\cuid_{1-b},\cSig_{1-b},\cscid_{1-b},\TYeval)\rbrace \\
          \pcreturn \cSig_b
        }

@@

\begin{figure}[ht!]
  \centering
  \scalebox{0.9}{
    \input{figures/nizk.tex}
  }
  \caption{CS specification of the NP relations used in \CUASGen.
  \todo{Is $\C = \CCommit(\usk;r)$ at Issue needed now that \upk is added?}}
  \label{fig:nizkrels}
\end{figure}

@@

\paragraph{$(\upk,\usk) \gets \UKeyGen(\parm)$.} %
Each user, prior to requesting credentials, generates his secret key by picking
randomly $\usk \getr \AttrSpace$. Set $\upk \gets \CCommit(\usk;0)$.
